### 2019-01-02 Sections/authors.tex
minor

\boldauthor{Zixin Huang}
%\email{zixin.huang@sheffield.ac.uk}
\smallaffiliation{Department of Physics \& Astronomy, University of Sheffield}

@@

\boldauthor{Tim Byrnes}
%\email{tim.byrnes@nyu.edu}
\smallaffiliation{State Key Laboratory of Precision Spectroscopy, School of Physical \& Material Sciences, East China Normal University, Shanghai 200062, China}
\smallaffiliation{NYU-ECNU Institute of Physics at NYU Shanghai, 3663 Zhongshan Road North, Shanghai 200062, China}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}
\smallaffiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China} 
\smallaffiliation{Department of Physics, New York University, New York, NY 10003, USA}

>>>>

\boldauthor{Zixin Huang}
%\email{zixin.huang@sheffield.ac.uk}
\smallaffiliation{Department of Physics \& Astronomy, University of Sheffield, United Kingdom}

@@

\boldauthor{Tim Byrnes}
%\email{tim.byrnes@nyu.edu}
\smallaffiliation{State Key Laboratory of Precision Spectroscopy, School of Physical \& Material Sciences, East China Normal University, Shanghai 200062, China}
\smallaffiliation{NYU-ECNU Institute of Physics at NYU Shanghai, 3663 Zhongshan Road North, Shanghai 200062, China}
\smallaffiliation{National Institute of Informatics, 2-1-2 Hitotsubashi, Chiyoda-ku, Tokyo 101-8430, Japan}
\smallaffiliation{New York University Shanghai, 1555 Century Ave, Pudong, Shanghai 200122, China} 
\smallaffiliation{Department of Physics, New York University, New York, NY 10003, United States}

### 2019-01-02 Sections/cloud_quantum_computing.tex
minor

\begin{figure}[!htpb]
	\includegraphics[clip=true, width=0.475\textwidth]{distributed_quantum_search}
	\captionspacefig \caption{Computational gain from adding a single extra node to a parallelised implementation of the quantum search algorithm.}\label{fig:dist_quant_search}
\end{figure}

>>>>

\begin{figure}[!htpb]
	\includegraphics[clip=true, width=0.475\textwidth]{distributed_quantum_search}
	\captionspacefig \caption{Computational gain from adding a single extra node to a parallelised implementation of the quantum search algorithm. Asymptotically, the computational benefit vanishes.}\label{fig:dist_quant_search}
\end{figure}
